
```{r, echo=FALSE}
diet <- 1
# Identify R plot color associated with diet of interest
gg_color_hue <- function(n) {
  hues = seq(15, 375, length=n+1)
  hcl(h=hues, l=65, c=100)[1:n]
}
color <- gg_color_hue(4)[diet]
```

## Focus: Diet `r diet`

### Individual growth curves

Plot individual chick growth curves, highlighting the results for chicks consuming Diet `r diet`.

```{r, echo=FALSE}
ggplot() +
  geom_line(data=ChickWeight, aes(x=Time, y=weight, color=Diet, group=Chick), alpha=.3) +
  geom_line(data=ChickWeight[Diet==diet], aes(x=Time, y=weight, color=Diet, group=Chick), size=0.7) +
  ggtitle(bquote(atop("Growth Curve for Individual Chicks",atop(italic(.(paste("Highlighted: Diet",diet)))))))
```

### Fitted growth curves

Plot fitted growth curves, highlighting the results for chicks consuming Diet `r diet`.

```{r, echo=FALSE, message=FALSE}
linesize <- rep(0.5,4)
linesize[diet] <- 1
ggplot() +
  geom_point(data=ChickWeight, aes(x=Time, y=weight, colour=Diet), alpha=.3, size=1.5) +
  geom_smooth(data=ChickWeight, aes(x=Time, y=weight, colour=Diet), alpha=.2) +
  geom_point(data=ChickWeight[Diet==diet], aes(x=Time, y=weight, colour=Diet), size=1.5) +
  geom_smooth(data=ChickWeight[Diet==diet], aes(x=Time, y=weight, colour=Diet), alpha=.2, size=.8) +
  guides(colour=guide_legend(override.aes=list(size=linesize, shape=c(NA,NA,NA,NA)))) +
  ggtitle(bquote(atop("Fitted Growth Curves",atop(italic(.(paste("Highlighted: Diet",diet)))))))
```

### Final weight density

Plot densities by diet for chicks' final weights (day 21), highlighting the results for chicks consuming Diet `r diet`.

```{r, echo=FALSE}
ggplot(ChickWeight[Time==21], aes(x=weight, colour=Diet)) +
    geom_density() +
    geom_density(data=ChickWeight[Time==21 & Diet==diet], aes(x=weight), fill=color, alpha=.2, show_guide=FALSE) +
  ggtitle(bquote(atop("Density: Final Weight",atop(italic(.(paste("Highlighted: Diet",diet)))))))
```


```{r, echo=FALSE}
diet <- 2
# Identify R plot color associated with diet of interest
gg_color_hue <- function(n) {
  hues = seq(15, 375, length=n+1)
  hcl(h=hues, l=65, c=100)[1:n]
}
color <- gg_color_hue(4)[diet]
```

## Focus: Diet `r diet`

### Individual growth curves

Plot individual chick growth curves, highlighting the results for chicks consuming Diet `r diet`.

```{r, echo=FALSE}
ggplot() +
  geom_line(data=ChickWeight, aes(x=Time, y=weight, color=Diet, group=Chick), alpha=.3) +
  geom_line(data=ChickWeight[Diet==diet], aes(x=Time, y=weight, color=Diet, group=Chick), size=0.7) +
  ggtitle(bquote(atop("Growth Curve for Individual Chicks",atop(italic(.(paste("Highlighted: Diet",diet)))))))
```

### Fitted growth curves

Plot fitted growth curves, highlighting the results for chicks consuming Diet `r diet`.

```{r, echo=FALSE, message=FALSE}
linesize <- rep(0.5,4)
linesize[diet] <- 1
ggplot() +
  geom_point(data=ChickWeight, aes(x=Time, y=weight, colour=Diet), alpha=.3, size=1.5) +
  geom_smooth(data=ChickWeight, aes(x=Time, y=weight, colour=Diet), alpha=.2) +
  geom_point(data=ChickWeight[Diet==diet], aes(x=Time, y=weight, colour=Diet), size=1.5) +
  geom_smooth(data=ChickWeight[Diet==diet], aes(x=Time, y=weight, colour=Diet), alpha=.2, size=.8) +
  guides(colour=guide_legend(override.aes=list(size=linesize, shape=c(NA,NA,NA,NA)))) +
  ggtitle(bquote(atop("Fitted Growth Curves",atop(italic(.(paste("Highlighted: Diet",diet)))))))
```

### Final weight density

Plot densities by diet for chicks' final weights (day 21), highlighting the results for chicks consuming Diet `r diet`.

```{r, echo=FALSE}
ggplot(ChickWeight[Time==21], aes(x=weight, colour=Diet)) +
    geom_density() +
    geom_density(data=ChickWeight[Time==21 & Diet==diet], aes(x=weight), fill=color, alpha=.2, show_guide=FALSE) +
  ggtitle(bquote(atop("Density: Final Weight",atop(italic(.(paste("Highlighted: Diet",diet)))))))
```


```{r, echo=FALSE}
diet <- 3
# Identify R plot color associated with diet of interest
gg_color_hue <- function(n) {
  hues = seq(15, 375, length=n+1)
  hcl(h=hues, l=65, c=100)[1:n]
}
color <- gg_color_hue(4)[diet]
```

## Focus: Diet `r diet`

### Individual growth curves

Plot individual chick growth curves, highlighting the results for chicks consuming Diet `r diet`.

```{r, echo=FALSE}
ggplot() +
  geom_line(data=ChickWeight, aes(x=Time, y=weight, color=Diet, group=Chick), alpha=.3) +
  geom_line(data=ChickWeight[Diet==diet], aes(x=Time, y=weight, color=Diet, group=Chick), size=0.7) +
  ggtitle(bquote(atop("Growth Curve for Individual Chicks",atop(italic(.(paste("Highlighted: Diet",diet)))))))
```

### Fitted growth curves

Plot fitted growth curves, highlighting the results for chicks consuming Diet `r diet`.

```{r, echo=FALSE, message=FALSE}
linesize <- rep(0.5,4)
linesize[diet] <- 1
ggplot() +
  geom_point(data=ChickWeight, aes(x=Time, y=weight, colour=Diet), alpha=.3, size=1.5) +
  geom_smooth(data=ChickWeight, aes(x=Time, y=weight, colour=Diet), alpha=.2) +
  geom_point(data=ChickWeight[Diet==diet], aes(x=Time, y=weight, colour=Diet), size=1.5) +
  geom_smooth(data=ChickWeight[Diet==diet], aes(x=Time, y=weight, colour=Diet), alpha=.2, size=.8) +
  guides(colour=guide_legend(override.aes=list(size=linesize, shape=c(NA,NA,NA,NA)))) +
  ggtitle(bquote(atop("Fitted Growth Curves",atop(italic(.(paste("Highlighted: Diet",diet)))))))
```

### Final weight density

Plot densities by diet for chicks' final weights (day 21), highlighting the results for chicks consuming Diet `r diet`.

```{r, echo=FALSE}
ggplot(ChickWeight[Time==21], aes(x=weight, colour=Diet)) +
    geom_density() +
    geom_density(data=ChickWeight[Time==21 & Diet==diet], aes(x=weight), fill=color, alpha=.2, show_guide=FALSE) +
  ggtitle(bquote(atop("Density: Final Weight",atop(italic(.(paste("Highlighted: Diet",diet)))))))
```


```{r, echo=FALSE}
diet <- 4
# Identify R plot color associated with diet of interest
gg_color_hue <- function(n) {
  hues = seq(15, 375, length=n+1)
  hcl(h=hues, l=65, c=100)[1:n]
}
color <- gg_color_hue(4)[diet]
```

## Focus: Diet `r diet`

### Individual growth curves

Plot individual chick growth curves, highlighting the results for chicks consuming Diet `r diet`.

```{r, echo=FALSE}
ggplot() +
  geom_line(data=ChickWeight, aes(x=Time, y=weight, color=Diet, group=Chick), alpha=.3) +
  geom_line(data=ChickWeight[Diet==diet], aes(x=Time, y=weight, color=Diet, group=Chick), size=0.7) +
  ggtitle(bquote(atop("Growth Curve for Individual Chicks",atop(italic(.(paste("Highlighted: Diet",diet)))))))
```

### Fitted growth curves

Plot fitted growth curves, highlighting the results for chicks consuming Diet `r diet`.

```{r, echo=FALSE, message=FALSE}
linesize <- rep(0.5,4)
linesize[diet] <- 1
ggplot() +
  geom_point(data=ChickWeight, aes(x=Time, y=weight, colour=Diet), alpha=.3, size=1.5) +
  geom_smooth(data=ChickWeight, aes(x=Time, y=weight, colour=Diet), alpha=.2) +
  geom_point(data=ChickWeight[Diet==diet], aes(x=Time, y=weight, colour=Diet), size=1.5) +
  geom_smooth(data=ChickWeight[Diet==diet], aes(x=Time, y=weight, colour=Diet), alpha=.2, size=.8) +
  guides(colour=guide_legend(override.aes=list(size=linesize, shape=c(NA,NA,NA,NA)))) +
  ggtitle(bquote(atop("Fitted Growth Curves",atop(italic(.(paste("Highlighted: Diet",diet)))))))
```

### Final weight density

Plot densities by diet for chicks' final weights (day 21), highlighting the results for chicks consuming Diet `r diet`.

```{r, echo=FALSE}
ggplot(ChickWeight[Time==21], aes(x=weight, colour=Diet)) +
    geom_density() +
    geom_density(data=ChickWeight[Time==21 & Diet==diet], aes(x=weight), fill=color, alpha=.2, show_guide=FALSE) +
  ggtitle(bquote(atop("Density: Final Weight",atop(italic(.(paste("Highlighted: Diet",diet)))))))
```


