---
title: "Reproducible Research Demo"
subtitle: "or: What Does This Code Do Again?"
author: 

  - name: Ben Chan
    affiliation: CHSE
    email: chanb@ohsu.edu
    
  - name: Stephanie Renfro
    affiliation: CHSE
    email: renfrst@ohsu.edu

  - name: Thomas Meath
    affiliation: CHSE
    email: meath@ohsu.edu
date: "`r format(Sys.time(), '%A, %d %B, %Y')`"
output: 
  html_document:
    template: 'H:/CodingProjects/CHSE_functions/chse/inst/rmarkdown/templates/CHSE_1/resources/default_chse.html'
    toc: true
    toc_depth: 3
    css: 'H:/CodingProjects/CHSE_functions/chse/inst/rmarkdown/templates/CHSE_1/resources/markdown.css'
  pdf_document:
    toc: TRUE

references:
- id: llama
  title: A systematic review of llama herding habits
  author:
  - family: McConnell
    given: K. John
  container-title: American Journal of Camelids
  volume: 21
  issue: 2
  publisher: National Livestock Publishing Group
  page: 124-198
  type: article-journal
  issued:
    year: 2014
    month: 10
---

## Purpose

This work was inspired by the following email from Farmer Ben.

> From: Ben Chan  
> Sent: Thursday, June 11, 2015 4:04 PM  
> To: Stephanie Renfro  
> Subject: What to feed chicks  
> 
> Hello,  
> 
> I'm receiving 20 baby chicks next month. Can you help me decide what to feed them? I'm choosing between the following four diets:  
> 
> 1.  Grower diet  
> 2.  Layer diet
> 3.	Breeder diet
> 4.	High cluckage diet  
> 
> Thanks,
> Ben
> 
> -----------------------------------------------------------------
> Ben Chan, Farmer and Research Associate  
> OHSU Center for Health Systems Effectiveness  
> Office: 3030 SW Moody | Mail Code: MDYCHSE  
> www.ohsu.edu/chse  



## Preliminaries

Start clock to calculate total runtime.

```{r}
start_program <- proc.time()
```

Load needed packages:

  * *data.table* - for faster processing  
  * *knitr* - for better tables ("kable" function)
  * *ggplot2* - for pretty plots  
  * *knitr* - for better table display    
  
```{r, warning=FALSE}
packages <- c("data.table", "ggplot2", "knitr")
sapply(packages, require, character.only=TRUE, quietly=TRUE)
```


## Prepare Data

This demo uses [data from an experiment on the effect of diet on early growth of chicks](http://www.inside-r.org/r-doc/datasets/ChickWeight), `ChickWeight`, which comes pre-loaded in any R session. Unfortunately, R does not come pre-loaded with a llama dataset[@llama].

Let's take a look at the first few rows:

```{r}
head(ChickWeight)
```

Let's also print a summary of the data.

*Note, by specifying the option "echo = FALSE", the resulting output will display, but not the code that generated it.*

```{r, echo=FALSE}
summary(ChickWeight)
```

Convert to data.table for faster processing.

```{r}
ChickWeight <- data.table(ChickWeight)
```

Just for fun, let's create a table showing mean weight at times 0, 10, and 21 days, for each of the four diet types.

```{r, results='asis'}
mean_ChickWeight <- ChickWeight[Time %in% c(0,10,21),
                                list(mean_weight = round(mean(weight), digits=1)),
                                by = list(Diet,Time)]

kable(mean_ChickWeight)
```

## Growth for Individual Chicks

**The following plot illustrates the growth curve for individual chicks from 0 to 21 days.**

Colors represent the four diets. From this plot, it is difficult to distinguish between the performance of the four diets. 

In subsequent plots, we focus our attention on a single diet.

```{r, echo=FALSE}
ggplot() +
  geom_line(data=ChickWeight, aes(x=Time, y=weight, color=Diet, group=Chick)) +
  ggtitle("Growth Curve for Individual Chicks")
```

```{r,echo=FALSE,warning=FALSE}
diet_list <- 1:4
brew::brew('ReproducibleResearchDemo_loop.brew','ReproducibleResearchDemo_loop.Rmd')
```

```{r, child="ReproducibleResearchDemo_loop.Rmd", eval=TRUE}
```

## Wrap Up

Calculate total runtime.

```{r}
time_program <- proc.time()-start_program
print(paste("Total runtime:", format(time_program[3]/60,digits=3), "minutes"))
```

Clear memory.

```{r}
rm(list=ls())
invisible(gc())
```

---------------------------------------------------------------

#Session Information#  

```{r,echo=FALSE,comment=NA,results='hold'}
#THIS CODE PRINTS YOUR SESSION INFO AT THE BOTTOM OF THE PAGE#
#PLEASE LEAVE THIS CODE IN#
cat("SESSION INFO\n")
cat("----------------------------------------------------\n")
print(sessionInfo(),locale=F)
```
  
#Works Cited#  
<br>  