---
title: "Reproducible Research Demo"
author: "OHSU Center for Health Systems Effectiveness"
date: "Wednesday, July 22, 2015"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
  word_document: default
---

Last update by Stephanie Renfro (<renfrst@ohsu.edu>) on `r paste(Sys.time())` using `r R.version.string`.


## Purpose

This work was inspired by the following email from Farmer Ben.

```
From: Ben Chan 
Sent: Thursday, June 11, 2015 4:04 PM
To: Stephanie Renfro
Subject: What to feed chicks

Hello,

I'm receiving 20 baby chicks next month. Can you help me decide what to feed them?

I'm choosing between the following four diets:

1.  Grower diet
2.  Layer diet
3.	Breeder diet
4.	High cluckage diet

Thanks,
Ben

-----------------------------------------------------------------
Ben Chan, Farmer and Research Associate
OHSU Center for Health Systems Effectiveness
Office: 3030 SW Moody | Mail Code: MDYCHSE
www.ohsu.edu/chse
```

\newpage

## Preliminaries

Start clock to calculate total runtime.

```{r}
start_program <- proc.time()
```

Load needed packages:

  * *data.table* - for faster processing
  * *knitr* - for better table display ("kable" function)
  * *ggplot2* - for pretty plots  
  
```{r, warning=FALSE}
packages <- c("data.table", "knitr", "ggplot2")
sapply(packages, require, character.only=TRUE, quietly=TRUE)
```

Define the CHSE color palette function.

```{r}
colorPalette <- function () {
  c(rgb(  1,  67, 134, maxColorValue=255),
    rgb(119, 120, 123, maxColorValue=255),
    rgb(139, 184, 234, maxColorValue=255),
    rgb(188, 190, 192, maxColorValue=255),
    rgb( 94, 122, 162, maxColorValue=255),
    rgb(223, 122,  28, maxColorValue=255))
}
```


## Prepare Data

This demo uses [data from an experiment on the effect of diet on early growth of chicks](http://www.inside-r.org/r-doc/datasets/ChickWeight), `ChickWeight`, which comes pre-loaded in any R session.

Let's take a look at the first few rows:

```{r}
head(ChickWeight)
```

Let's also print a summary of the data.

*Note, by specifying the option "echo = FALSE", the resulting output will display, but not the code that generated it.*

```{r, echo=FALSE}
summary(ChickWeight)
```

Convert to data.table for faster processing.

```{r}
ChickWeight <- data.table(ChickWeight)
```

Create a table showing mean weight at times 0, 10, and 21 days, for each of the four diet types.

```{r, results='asis'}
mean_ChickWeight <- ChickWeight[Time %in% c(0,10,21),
                                list(mean_weight = round(mean(weight), digits=1)),
                                by = list(Diet,Time)]

kable(mean_ChickWeight)
```

Create a character variable for `diet`.
Use this variable for plotting small multiples.

```{r}
ChickWeight[, dietChr := sprintf("Diet %d", Diet)]
```


## Growth for Individual Chicks

The following plot illustrates the growth curve for individual chicks from 0 to 21 days.

Colors represent the four diets. 

```{r}
ggplot() +
  geom_line(data=ChickWeight, aes(x=Time, y=weight, color=dietChr, group=Chick)) +
  scale_color_manual(values=colorPalette()) +
  ggtitle("Growth Curve for Individual Chicks")

```

**From this plot, it is difficult to distinguish between the performance of the four diets.**

\newpage

### Individual growth curves

Plot individual chick growth curves using small multiples.

```{r}
ggplot() +
  geom_line(data=ChickWeight, aes(x=Time, y=weight, color=dietChr, group=Chick)) +
  facet_wrap(~ dietChr, nrow=1) + 
  scale_color_manual(values=colorPalette()) +
  theme(legend.position="none") +
  ggtitle(bquote(atop("Growth Curve for Individual Chicks")))
```

\newpage

### Fitted growth curves

Plot fitted growth curves using small multiples.
Data points are jittered around time value.

```{r, message=FALSE}
ggplot() +
  geom_jitter(data=ChickWeight, aes(x=Time, y=weight, colour=dietChr)) +
  geom_smooth(data=ChickWeight, aes(x=Time, y=weight, colour=dietChr)) +
  facet_wrap(~ dietChr, nrow=1) + 
  scale_color_manual(values=colorPalette()) +
  theme(legend.position="none") +
  ggtitle(bquote(atop("Fitted Growth Curves")))
```

\newpage

### Final weight density

Plot densities by diet for chicks' final weights (day 21) using small multiples.

```{r}
ggplot(ChickWeight[Time==21], aes(x=weight, colour=dietChr, fill=dietChr)) +
    geom_density() +
  facet_wrap(~ dietChr, nrow=4) + 
  scale_color_manual(values=colorPalette()) +
  scale_fill_manual(values=colorPalette()) +
  theme(legend.position="none") +
  ggtitle(bquote(atop("Density: Final Weight")))
```


## Wrap Up

Calculate total runtime and clear memory.

```{r}
time_program <- proc.time()-start_program
print(paste("Total runtime:", format(time_program[3]/60,digits=3), "minutes"))
rm(list=ls())
invisible(gc())
```
